---
title: "Reanalysis of nGBR harvest models"
output: html_notebook
---

```{r}
rm(list=ls())
#library(nloptr)
library(Rsolnp)
library(tidyverse)
```

Define functions first. 

Our model has 6 stages (email from NF on 2019-11-19)
1- neonate to 1 year (eggs, hatchlings, post hatchlings)
2- pelagic juveniles
3- benthic juveniles (up to 65cm)
4- subadults (>65 cm to 86cm)
5- maturing adults (>85 to 95 cm)
6- adults (>95 cm)

```{r}
# Create a function to define Lefkovitch matrix. 
# Ts is the stage durations of various juvenile stages  (T in Caswell's book) - the last stage is assumed to be maturing adults, so their fecundity is not zero.
# VT is a vector variances of stage durations
# f is a vector of fertilities (this excludes the survival of adult): only two are allowed
# only maturing adults (MA) and adults (A) breed. 
# phi.J includes pelagic juvenile, neritic juvenile, subadult, and maturing adult stages. 
# p.breed is a vector of proportions of maturing - same length as f
define.matrix <- function(Ts, VT, f, phi.1, phi.J, phi.A, p.breed){
  gam <- Ts/(VT + Ts)   # probability of moving to the next stage.
  k <- round((Ts^2) / (VT + Ts))
  M.dim <- sum(k) + 2
  
  # juvenile + subadult stages + maturing adults (ks) + adult stages (length of fecundity) + first year
  M <- matrix(data = 0, 
              nrow = M.dim, 
              ncol = M.dim)
  
  # all pseudo stages for the maturing adult stage need to reproduce (Caswell 2001, p. 165)
  # fertility needs survival for the post-breeding census
  M[1, M.dim] <- f[2] * phi.A * p.breed[2]  # adults
  M[1, (M.dim - k[length(Ts)]):(M.dim - 1)] <- f[1] * phi.J[length(phi.J)] * p.breed[1] 
  
  M[2, 1] <- phi.1
  M[M.dim, M.dim] <- phi.A

  # fill in two rows for each column staying (1 - gam) and leaving (gam)
  l <- 1  
  for (j in 1:length(k)){
    for (i in 1:k[j]){
      M[(l + 1), (l + 1)] <- phi.J[j] * (1 - gam[j])
      M[(l + 2), (l + 1)] <- phi.J[j] * gam[j]
      l <- l + 1
    }
    
  }

  # compute eigenvalues
  eig1 <- eigen(M)
  
  # return stuff.
  return(list(k = k,
              gam = gam,
              phi.J = phi.J,
              M = M,
              eigen1 = eig1$values[1]))
}


# the inequality constraints didn't work so well in nloptr package.
# estim <- nloptr(x0 = c(0.5, 0.7, 0.9),
#                 eval_f = obj.fcn,
#                 eval_g_ineq = eval_g0,
#                 lb = c(0,0,0), 
#                 ub = c(1.0,1.0,1.0),
#                 opts = list("algorithm" = "NLOPT_LN_COBYLA",
#                             "xtol_abs" = c(1.0e-18, 1.0e-18, 1.0e-18),
#                             "maxeval" = 50000))

#"NLOPT_LN_NELDERMEAD" - worked for without contraint
#"NLOPT_GN_AGS" - does not work
#"NLOPT_GN_ORIG_DIRECT" - didn't work so well. 
#                            ,
#                            "maxeval" = 10000

# Tried to use matrix algebra but didn't work so well in nloptr package... 
# eval_g0 <- function(x){
#   return(matrix(c(1,-1,0,0,1,-1), nrow = 2, ncol = 3) %*% c(x[1], x[2], x[3]))
# }

# Using Rsolnp package - this seems to work better. in.list needs to be available in the workspace.

obj.fcn <- function(x){
  M <- define.matrix(Ts = in.list$Ts, 
                     VT = in.list$VT, 
                     f = in.list$f, 
                     phi.1 = in.list$phi.1, 
                     phi.J = x, 
                     phi.A = in.list$phi.A,
                     p.breed = in.list$p.breed)
  
  eig.1 <- M$eigen1
  
  return(abs(eig.1 - in.list$lambda))
}

# Differences of survival rates between two subsequent stages
# are always negative = increasing survival rates
eval_g0 <- function(x){
  
  return(c(x[1] - x[2], x[2] - x[3], x[3] - x[4]))
}

```


The purpose of the study was to determine effects of various factors on the future of the nGBR population of green turtles. Consequently, we needed to develop various projection matrices depending on various assumptions. 

This document describes the analysis of computing the missing juvenile survival and transition probabilities for green turtles in nGBR. In this analysis, we constract Lefkovitch matrices with the assumption of postbreeding census. The input demographic paramters are as follows. Because we do not have empirical estimates of juvenile survival and transition probabilities, they need to be determined. In this study, we use the negative binomial model in Caswell (2001, pp. 164-165). The negative binomial model creates pseudo stages so that individuals in one stage are slowed down to move to the next stage.  Although juvenile suvival rates can be any value between 0 and 1, with some constraints for a projection matrix, these values can be narrowed down. In our analysis, we made various scenarios about how the population may grow.  The population growth rate of a projection matrix is equal to the dominant eigenvalue of the matrix.  We assumed that survival rates will increase with age (stage).  Given these two constraints (i.e., fixed dominant eigenvalue and increasing survival rates) along with the negative binomial model, we determined the juvenile survival rates and transition probabilities numerically. 

All analyses were conducted in the statistical package R (v. 3.6.1, R Development Team). Numerical optimizations were conducted using *Rsolnp* package (Alexios Ghalanos and Stefan Theussl (2015). Rsolnp: General Non-linear Optimization Using Augmented Lagrange Multiplier Method. R package version 1.16.)     

In the negative binomial model of Caswell (2001), the mean and variance of stage durations are needed. We used the values found in published papers (mostly from one paper by Chaloupka M. 2002. Stohastic simulation modelling of southern Great Barrier Reef green turtle population dynamics. Ecological Modelling 148:79-109).  

(The following was adapted from email from NF on 2019-11-18 and around that date.)
### Stage durations

#### Age class 1: This first stage includes eggs, hatchlings, and neonates (until the end of the next nesting season). 

#### Pelagic juvenile: mean = 4 yrs., SD = 0 (Chaloupka 2002) 
Although Chaloupka (2002) did not provide the uncertainty for the mean, he stated that "Age-class 2 comprises the pelagic juvenile phase that occurs in southwestern Pacific gyres or along convergence zones (Carr A. 1987. New perspectives on the pelagic stage of sea turtle development. Conservation Biology 1:103-121). Excluding ageclass 1, mean pelagic juvenile ageclass duratoin for green sea turtles has been estimated approximately 4-5 years (Limpus CJ and Chaloupka M 1997. Nonparametric regression modelling of green sea turtle growth rates (southern Great Barrier Reef). Marine Ecology Progress Series 149:23-34, Zug GR and Glor RE 1998. Estimates of age and growth in a population of green sea turtles (*Chelonia mydas*) from the Indian River lagoon system, Florida: a skeletochronological analysis. Canadian Journal of Zoology 76:1497-1506.)." Consequently, we used variance of 1.

#### Benthic juvenile: mean = 5 yrs., SD = 1
Based on the growth of nGBR green turtles (Chaloupka et al. 2004), we determined that this stage should last about 5 years. Although we did not have an estimate of variability around this mean, we speculated that variability of 1 year would be appropriate. 

After these years (10 years on average), turtles become subadults.

#### Subadult: mean = 19 yrs., SD = 1.9 (Chaloupka 2002)

These values come from Chaloupka (2002). 

#### Matruing adult: mean = 5 yrs, SD = 1 (Chaloupka 2002)

We assumed 12% of maturing adults nest annually. (REF?)


### Survival rates

We consider four sources of mortality for the first year. 

#### Egg survival to hatchling emergence (includes mortality from inundation, erosion) = 0.685  (from Bramble Cay 1979-1980)

Using this as a basis for estimating nGBR emergence success
I can't find the calculations used for emergence success - I had not realised that the emergence success Col reports for Raine Is (Limpus et al 2003) only includes nests that successfully produced hatchlings- not any of the inundated nests with zero success - so it is a substantial underestimate. The original value of 78.8% (however calculated) has to be too high.

The most reliable estimate of emergent success from (only) successful nests was from 1984 when 162 nests were surveyed    78.6%   s.e.= 15.21  (Limpus et al 2003)

At Bramble Cay, Limpus, Carter and Hamann (2001) track nests throughout the 1979-1980 season and their emergence success accounts for unsuccessful nests
emergence success = 68.5% 
I think that would be a better number to use-  although it is from nearly 40 years ago, so a bit hard to justify.  

It would be better to use more recent data from Raine Is if you have access to that.

#### Hatchling survival across beach = 0.99 (no published value, see comments below)

available data are for survival from nest to water from Limpus et al (2003) and Limpus (2008) who provides this info 

other than Raine Is, expected mortality <2%

highly variable at Raine Is- predation can be quite high April 1984 with 20.5 clutches per night, in a year with 1000s of rufous night herons breeding  - hatchling survival only 6.7%
in contrast June 1980, with 100s of herons, for the 11 clutches watched, hatchling survival = 99.3%

For an optimistic estimate we could set it to 99.0 % survival

#### Hatchling survival across reef flat = 0.69  (from Gyuris)

available data are for survival across reef flat at Heron Island (Gyuris 1994)
mean predation was 31% s.e. = 2.5%  
so survival  = 69%

#### Post hatchling survival = 0.95, s.d. = 0.01  (from Chaloupka 2002)  

(that seems a bit optimistic) 

Although the post hatchling survival was determined to be 0.95 (SD = 0.01) in Chaloupka (2002), this value seems too optimistic because this is significantly higher than the next stage (0.65 SD = 0.005; Chaloupka 2002, Table 1).  I think it makes more sense to use the survival rate for the next stage (0.65) than using this arbitrary value. 

Using all these information, we arrive at 0.445 (using the unlikely 0.95) or 0.3 (using the more likely but probably still too high at 0.64). 

1 yr survival = 0.685 x 0.99 x 0.69 x 0.95 = 0.445

1 yr survival = 0.685 x 0.99 x 0.69 x 0.64 = 0.3

#### Juvenile survival rates (Chaloupka 2002)

Pelagic juvenile: 0.64 (SD = 0.005)

Benthic juvenile: 0.88 (SD = 0.006)

Subadult: 0.85 (SD = 0.01)


#### Adult survival rate

Somewhere between 0.9287 and 0.96  (sorry, not much help)

NOTES
Chaloupka (2002) used 0.9482 s.d. 0.005 for sGBR based on Heron Reef data

But in his 2003 report to GBRMPA on the sGBR he used the value 0.96

When Mick derived an estimate based on Shoalwater Bay data  = 0.9287, which we use in the Shoalwater matrix
Mick also estimated adult survival for Clack Reef based on the field data as 0.98, which he thought was too high and given a 95% C.I. or 0.96-1.0 he recommended using 0.96, but he was not confident there was sufficient field data. 

### Fertility

Fertility of green turtles is affected by the number of eggs per nest, the number of nests per female per nesting season, remigration intervals, and survival rates. The following values were used for this study.

eggs /nest= 103.9  (Raine Is, Limpus et al 2003)

nests/female = 6.2  (Raine Is, Limpus et al 2003)

remigation interval = 5.35 yr  (Raine Is, Limpus et al 2003)

#### First year breeder (a.k.a., maturing adult)
The fecundity for the maturing adult stage is computed as the following: Eggs/nests (103.9) x nests/female (6.2) x (1/remigration interval) (1/5.35) x sex ratio (see below). This is also an unknown as the maturing adult survival rate is unknown.  

Proportion of breeding females is included at the time of creating fertility later.

Base: 103.9 x 6.2 x (1/5.35) x 0.8 = 96.3

Modelrate climate: 103.9 x 6.2 x (1/5.35) x 0.88 = 106.0

Extreme climate: 103.9 x 6.2 x (1/5.35) x 0.99 = 119.2

#### Adult
For the adults, we replace the proportion of the 1st year breeder that nest with the remigration interval: Eggs/nests x nests/female x (1/remigration interval) (1/5.35) 

Base: 103.9 x 6.2 x (1/5.35) x 0.8 = 96.3

Moderate climate: 103.9 x 6.2 x (1/5.35) x 0.88 = 106.0

Extreme climate: 103.9 x 6.2 x (1/5.35) x 0.99 = 119.2

### Sex ratio

We evaluated the following scenarios for sex ratios. 

base: 80% female

moderate climate: 88% female

extreme climate: 99% female


I confine the parameter space for juvenile and subadult survival rates to the following:
pelagic juvenile = [0.1, 0.8]
benthic juvenile = [0.1, 0.9]
subadult = [0.5, 0.95]


## Base case
In the base case scenarios, we set the sex ratio to be 0.8.  Within the base case, we evaulate three different growth rates (dominant eigenvalue); 0.95, 1.0, and 1.04. 

### lambda = 0.95

These bounds come from our knowledge of green turtles as well as common sense. 

```{r message=FALSE}
# Define demographic parameters
in.list <- list(Ts = c(5, 5, 19, 5),   # average years in two juvenile stages and subadults
                VT =  c(1, 1, (1.9^2), 1),  # variance of years in two juvenile stages 
                f =  c(96.3, 96.3), # 
                phi.1 =  0.3,
                phi.A = 0.95,
                p.breed = c(0.12, 1.0),
                lambda = 0.95)

# find the juvenile survival and transition probabilities
estim.base.095 <- gosolnp(fun = obj.fcn,
                          ineqfun = eval_g0,
                          LB = c(0.1, 0.1, 0.3, 0.5), 
                          UB = c(0.8, 0.9, 0.95, 0.95),
                          ineqLB = c(-1.0, -1.0, -1.0),
                          ineqUB = c(0.0, 0.0, 0.0),
                          distr = c(1,1,1,1),
                          control = list(outer.iter = 5000,
                                         inner.iter = 10000,
                                         tol = 1.0e-15,
                                         delta = 1.0e-12))

```

Using these derived survival rates, we derive a Lefkovitch matrix using the negative binomial model. 

```{r}
in.list$phi.J <- estim.base.095$pars
M.base.095 <- define.matrix(Ts = in.list$Ts, 
                            VT = in.list$VT, 
                            f = in.list$f, 
                            phi.1 = in.list$phi.1, 
                            phi.J = in.list$phi.J, 
                            phi.A = in.list$phi.A,
                            p.breed = in.list$p.breed)

write.table(M.base.095$M, 
            file = "data/Base_095.csv",
            row.names = F,
            col.names = FALSE,
            sep = ",")

#M.base.095
```

### lambda = 1.00

```{r message=FALSE}
# Define demographic parameters
in.list <- list(Ts = c(5, 5, 19, 5),   # average years in two juvenile stages and subadults
                VT =  c(1, 1, (1.9^2), 1),  # variance of years in two juvenile stages 
                f =  c(96.3, 96.3), # 
                phi.1 =  0.4,
                phi.A = 0.95,
                p.breed = c(0.12, 1.0),
                lambda = 1.00)

# find the juvenile survival and transition probabilities
estim.base.100 <- gosolnp(fun = obj.fcn,
                          ineqfun = eval_g0,
                          LB = c(0.1, 0.1, 0.3, 0.5), 
                          UB = c(0.8, 0.9, 0.95, 0.95),
                          ineqLB = c(-1.0, -1.0, -1.0),
                          ineqUB = c(0.0, 0.0, 0.0),
                          distr = c(1,1,1,1),
                          control = list(outer.iter = 5000,
                                         inner.iter = 10000,
                                         tol = 1.0e-15,
                                         delta = 1.0e-12))

```

Using these derived survival rates, we derive a Lefkovitch matrix using the negative binomial model. 

```{r}
in.list$phi.J <- estim.base.100$pars
M.base.100 <- define.matrix(Ts = in.list$Ts, 
                            VT = in.list$VT, 
                            f = in.list$f, 
                            phi.1 = in.list$phi.1, 
                            phi.J = in.list$phi.J, 
                            phi.A = in.list$phi.A,
                            p.breed = in.list$p.breed)

write.table(M.base.100$M, 
            file = "data/Base_100.csv",
            row.names = F,
            col.names = FALSE,
            sep = ",")

#M.base.100
```

### lambda = 1.04

```{r echo=FALSE, message=FALSE}
# Define demographic parameters
in.list <- list(Ts = c(5, 5, 19, 5),   # average years in two juvenile stages and subadults
                VT =  c(1, 1, (1.9^2), 1),  # variance of years in two juvenile stages 
                f =  c(96.3, 96.3), # 
                phi.1 =  0.4,
                phi.A = 0.95,
                p.breed = c(0.12, 1.0),
                lambda = 1.04)

# find the juvenile survival and transition probabilities
estim.base.104 <- gosolnp(fun = obj.fcn,
                          ineqfun = eval_g0,
                          LB = c(0.1, 0.1, 0.3, 0.5), 
                          UB = c(0.8, 0.9, 0.95, 0.95),
                          ineqLB = c(-1.0, -1.0, -1.0),
                          ineqUB = c(0.0, 0.0, 0.0),
                          distr = c(1,1,1,1),
                          control = list(outer.iter = 5000,
                                         inner.iter = 10000,
                                         tol = 1.0e-15,
                                         delta = 1.0e-12))

```

Using these derived survival rates, we derive a Lefkovitch matrix using the negative binomial model. 

```{r}
in.list$phi.J <- estim.base.104$pars
M.base.104 <- define.matrix(Ts = in.list$Ts, 
                            VT = in.list$VT, 
                            f = in.list$f, 
                            phi.1 = in.list$phi.1, 
                            phi.J = in.list$phi.J, 
                            phi.A = in.list$phi.A,
                            p.breed = in.list$p.breed)

write.table(M.base.104$M, 
            file = "data/Base_104.csv",
            row.names = F,
            col.names = FALSE,
            sep = ",")
#M.base.104
```

## Moderate climate case
In the moderate-climate case scenarios, we set the sex ratio to be 0.88.  Within the base case, we evaulate three different growth rates (dominant eigenvalue); 0.95, 1.0, and 1.04. 

### lambda = 0.95

```{r message=FALSE}
# Define demographic parameters
in.list <- list(Ts = c(5, 5, 19, 5),   # average years in two juvenile stages and subadults
                VT =  c(1, 1, (1.9^2), 1),  # variance of years in two juvenile stages 
                f =  c(106.0, 106.0), # 
                phi.1 =  0.4,
                phi.A = 0.95,
                p.breed = c(0.12, 1.0),
                lambda = 0.95)

# find the juvenile survival and transition probabilities
estim.moderate.095 <- gosolnp(fun = obj.fcn,
                              ineqfun = eval_g0,
                              LB = c(0.1, 0.1, 0.3, 0.5), 
                              UB = c(0.8, 0.9, 0.95, 0.95),
                              ineqLB = c(-1.0, -1.0, -1.0),
                              ineqUB = c(0.0, 0.0, 0.0),
                              distr = c(1,1,1,1),
                              control = list(outer.iter = 5000,
                                             inner.iter = 10000,
                                             tol = 1.0e-15,
                                             delta = 1.0e-12))

```

Using these derived survival rates, we derive a Lefkovitch matrix using the negative binomial model. 

```{r}
in.list$phi.J <- estim.moderate.095$pars
M.moderate.095 <- define.matrix(Ts = in.list$Ts, 
                                VT = in.list$VT, 
                                f = in.list$f, 
                                phi.1 = in.list$phi.1, 
                                phi.J = in.list$phi.J, 
                                phi.A = in.list$phi.A,
                                p.breed = in.list$p.breed)

write.table(M.moderate.095$M, 
            file = "data/Moderate_095.csv",
            row.names = F,
            col.names = FALSE,
            sep = ",")
#M.moderate.095
```

### lambda = 1.00

```{r message=FALSE}
# Define demographic parameters
in.list <- list(Ts = c(5, 5, 19, 5),   # average years in two juvenile stages and subadults
                VT =  c(1, 1, (1.9^2), 1),  # variance of years in two juvenile stages 
                f =  c(106.0, 106.0), # 
                phi.1 =  0.4,
                phi.A = 0.95,
                p.breed = c(0.12, 1.0),
                lambda = 1.00)

# find the juvenile survival and transition probabilities
estim.moderate.100 <- gosolnp(fun = obj.fcn,
                              ineqfun = eval_g0,
                              LB = c(0.1, 0.1, 0.3, 0.5), 
                              UB = c(0.8, 0.9, 0.95, 0.95),
                              ineqLB = c(-1.0, -1.0, -1.0),
                              ineqUB = c(0.0, 0.0, 0.0),
                              distr = c(1,1,1,1),
                              control = list(outer.iter = 5000,
                                             inner.iter = 10000,
                                             tol = 1.0e-15,
                                             delta = 1.0e-12))

```

Using these derived survival rates, we derive a Lefkovitch matrix using the negative binomial model. 

```{r}
in.list$phi.J <- estim.moderate.100$pars
M.moderate.100 <- define.matrix(Ts = in.list$Ts, 
                                VT = in.list$VT, 
                                f = in.list$f, 
                                phi.1 = in.list$phi.1, 
                                phi.J = in.list$phi.J, 
                                phi.A = in.list$phi.A,
                                p.breed = in.list$p.breed)

write.table(M.moderate.100$M, 
            file = "data/Moderate_100.csv",
            row.names = F,
            col.names = FALSE,
            sep = ",")

#M.moderate.100
```

### lambda = 1.04

```{r echo=FALSE, message=FALSE}
# Define demographic parameters
in.list <- list(Ts = c(5, 5, 19, 5),   # average years in two juvenile stages and subadults
                VT =  c(1, 1, (1.9^2), 1), # variance of years in two juvenile stages 
                f =  c(106.0, 106.0), # 
                phi.1 =  0.4,
                phi.A = 0.95,
                p.breed = c(0.12, 1.0),
                lambda = 1.04)

# find the juvenile survival and transition probabilities
estim.moderate.104 <- gosolnp(fun = obj.fcn,
                              ineqfun = eval_g0,
                              LB = c(0.1, 0.1, 0.3, 0.5), 
                              UB = c(0.8, 0.9, 0.95, 0.95),
                              ineqLB = c(-1.0, -1.0, -1.0),
                              ineqUB = c(0.0, 0.0, 0.0),
                              distr = c(1,1,1,1),
                              control = list(outer.iter = 5000,
                                             inner.iter = 10000,
                                             tol = 1.0e-15,
                                             delta = 1.0e-12))

```

Using these derived survival rates, we derive a Lefkovitch matrix using the negative binomial model. 

```{r}
in.list$phi.J <- estim.moderate.104$pars
M.moderate.104 <- define.matrix(Ts = in.list$Ts, 
                                VT = in.list$VT, 
                                f = in.list$f, 
                                phi.1 = in.list$phi.1, 
                                phi.J = in.list$phi.J, 
                                phi.A = in.list$phi.A,
                                p.breed = in.list$p.breed)

write.table(M.moderate.104$M, 
            file = "data/Moderate_104.csv",
            row.names = F,
            col.names = FALSE,
            sep = ",")

#M.moderate.104
```


## Extreme climate case
In the moderate-climate case scenarios, we set the sex ratio to be 0.99.  Within the base case, we evaulate three different growth rates (dominant eigenvalue); 0.95, 1.0, and 1.04. 

### lambda = 0.95

These bounds come from our knowledge of green turtles as well as common sense. 

```{r message=FALSE}
# Define demographic parameters
in.list <- list(Ts = c(5, 5, 19, 5),   # average years in two juvenile stages and subadults
                VT =  c(1, 1, (1.9^2), 1),  # variance of years in two juvenile stages 
                f =  c(119.2, 119.2), # 
                phi.1 =  0.4,
                phi.A = 0.95,
                p.breed = c(0.12, 1.0),
                lambda = 0.95)

# find the juvenile survival and transition probabilities
estim.extreme.095 <- gosolnp(fun = obj.fcn,
                             ineqfun = eval_g0,
                             LB = c(0.1, 0.1, 0.3, 0.5), 
                             UB = c(0.8, 0.9, 0.95, 0.95),
                             ineqLB = c(-1.0, -1.0, -1.0),
                             ineqUB = c(0.0, 0.0, 0.0),
                             distr = c(1,1,1,1),
                             control = list(outer.iter = 5000,
                                            inner.iter = 10000,
                                            tol = 1.0e-15,
                                            delta = 1.0e-12))

```

Using these derived survival rates, we derive a Lefkovitch matrix using the negative binomial model. 

```{r}
in.list$phi.J <- estim.extreme.095$pars
M.extreme.095 <- define.matrix(Ts = in.list$Ts, 
                               VT = in.list$VT, 
                               f = in.list$f, 
                               phi.1 = in.list$phi.1, 
                               phi.J = in.list$phi.J, 
                               phi.A = in.list$phi.A,
                               p.breed = in.list$p.breed)

write.table(M.extreme.095$M, 
            file = "data/Extreme_095.csv",
            row.names = F,
            col.names = FALSE,
            sep = ",")

#M.extreme.095
```

### lambda = 1.00

```{r message=FALSE}
# Define demographic parameters
in.list <- list(Ts = c(5, 5, 19, 5),   # average years in two juvenile stages and subadults
                VT =  c(1, 1, (1.9^2), 1),  # variance of years in two juvenile stages 
                f =  c(119.2, 119.2), # 
                phi.1 =  0.4,
                phi.A = 0.95,
                p.breed = c(0.12, 1.0),
                lambda = 1.00)

# find the juvenile survival and transition probabilities
estim.extreme.100 <- gosolnp(fun = obj.fcn,
                             ineqfun = eval_g0,
                             LB = c(0.1, 0.1, 0.3, 0.5), 
                             UB = c(0.8, 0.9, 0.95, 0.95),
                             ineqLB = c(-1.0, -1.0, -1.0),
                             ineqUB = c(0.0, 0.0, 0.0),
                             distr = c(1,1,1,1),
                             control = list(outer.iter = 5000,
                                            inner.iter = 10000,
                                            tol = 1.0e-15,
                                            delta = 1.0e-12))

```

Using these derived survival rates, we derive a Lefkovitch matrix using the negative binomial model. 

```{r}
in.list$phi.J <- estim.extreme.100$pars
M.extreme.100 <- define.matrix(Ts = in.list$Ts, 
                               VT = in.list$VT, 
                               f = in.list$f, 
                               phi.1 = in.list$phi.1, 
                               phi.J = in.list$phi.J, 
                               phi.A = in.list$phi.A,
                               p.breed = in.list$p.breed)

write.table(M.extreme.100$M, 
            file = "data/Extreme_100.csv",
            row.names = F,
            col.names = FALSE,
            sep = ",")

#M.extreme.100
```

### lambda = 1.04

```{r echo=FALSE, message=FALSE}
# Define demographic parameters
in.list <- list(Ts = c(5, 5, 19, 5),   # average years in two juvenile stages and subadults
                VT =  c(1, 1, (1.9^2), 1),  # variance of years in two juvenile stages 
                f =  c(119.2, 119.2), # 
                phi.1 =  0.4,
                phi.A = 0.95,
                p.breed = c(0.12, 1.0),
                lambda = 1.04)

# find the juvenile survival and transition probabilities
estim.extreme.104 <- gosolnp(fun = obj.fcn,
                             ineqfun = eval_g0,
                             LB = c(0.1, 0.1, 0.3, 0.5), 
                             UB = c(0.8, 0.9, 0.95, 0.95),
                             ineqLB = c(-1.0, -1.0, -1.0),
                             ineqUB = c(0.0, 0.0, 0.0),
                             distr = c(1,1,1,1),
                             control = list(outer.iter = 5000,
                                            inner.iter = 10000,
                                            tol = 1.0e-15,
                                            delta = 1.0e-12))

```

Using these derived survival rates, we derive a Lefkovitch matrix using the negative binomial model. 

```{r}
in.list$phi.J <- estim.extreme.104$pars
M.extreme.104 <- define.matrix(Ts = in.list$Ts, 
                               VT = in.list$VT, 
                               f = in.list$f, 
                               phi.1 = in.list$phi.1, 
                               phi.J = in.list$phi.J, 
                               phi.A = in.list$phi.A,
                               p.breed = in.list$p.breed)

write.table(M.extreme.104$M, 
            file = "data/Extreme_104.csv",
            row.names = F,
            col.names = FALSE,
            sep = ",")

#M.extreme.104
```

These are one of many possible combinations of survival rates.  





